---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinyPSDE: Shiny Police Shooting Data Explorer - WIP

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of shinyPSDE is to serve as a data explorer for the Washington Post Police Shooting Database.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/shinyPSDE")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(shinyPSDE)
## basic example code
shinyPSDE::run_app()
```

## Credit

Credit goes to the Washington Post and their research and reporting/database development team for compiling and sharing the dataset on their [Github repo](https://github.com/washingtonpost/data-police-shootings).

### Note

The data used in this app was originally published under an Attribution-NonCommercial-ShareAlike 4.0 International (CC BY-NC-SA 4.0) license.